Report on Effect Size Translation

### 2020-10-27 report.Rmd
Cleaned up rmd

converted_data %>%
  group_by(std_eff_name) %>%
  summarize(Mean = mean(value_consensus_r),
            SD = sd(value_consensus_r),
            Min = min(value_consensus_r),
            Max = max(value_consensus_r)) %>%
  gt() %>%
  tab_header(
    title = "Effect Size Summary",
    subtitle = "Descriptives by Effect Size Type"
  ) %>%
  fmt_number(columns = 2:5,
             decimals = 3)

@@

# Project Structure
```{r}
targets::tar_glimpse()
```

>>>>

converted_data %>%
  group_by(std_eff_name) %>%
  summarize(Mean = mean(value_consensus_r, na.rm = TRUE),
            SD = sd(value_consensus_r, na.rm = TRUE),
            Min = min(value_consensus_r, na.rm = TRUE),
            Max = max(value_consensus_r, na.rm = TRUE)) %>%
  gt() %>%
  tab_header(
    title = "Effect Size Summary",
    subtitle = "Descriptives by Effect Size Type"
  ) %>%
  fmt_number(columns = 2:5,
             decimals = 3)

@@

# Project Structure
```{r}
targets::tar_visnetwork()
```
